### 2024-09-02 cognitive-bias.qmd
20240902 - fix error

simulationOfFlippingCoins <- simulationOfFlippingCoins %>% 
  mutate(
    proportionHeadsSmallNumFlips = numHeadsSmallNumFlips / smallNumFlips,
    proportionHeadsLargeNumFlips = numHeadsLargeNumFlips / largeNumFlips,
    highlight = ifelse(numHeads == 5, "yes", "no"),
    extremeSmallNumFlips = ifelse(proportionHeadsSmallNumFlips <= 0.2 | proportionHeadsSmallNumFlips >= 0.8, TRUE, FALSE),
    extremeLargeNumFlips = ifelse(proportionHeadsLargeNumFlips <= 0.2 | proportionHeadsLargeNumFlips >= 0.8, TRUE, FALSE),
  )

>>>>

simulationOfFlippingCoins <- simulationOfFlippingCoins %>% 
  mutate(
    proportionHeadsSmallNumFlips = numHeadsSmallNumFlips / smallNumFlips,
    proportionHeadsLargeNumFlips = numHeadsLargeNumFlips / largeNumFlips,
    highlight = ifelse(numHeadsSmallNumFlips == 5, "yes", "no"),
    extremeSmallNumFlips = ifelse(proportionHeadsSmallNumFlips <= 0.2 | proportionHeadsSmallNumFlips >= 0.8, TRUE, FALSE),
    extremeLargeNumFlips = ifelse(proportionHeadsLargeNumFlips <= 0.2 | proportionHeadsLargeNumFlips >= 0.8, TRUE, FALSE),
  )
